---
title: "Contrast Effects on Architecture in Change Detection"
site: workflowr::wflow_site
output:
  workflowr::wflow_html:
    toc: true
editor_options:
  chunk_output_type: console
---

David Mussoff, Anthea G. Blunden, and Daniel R. Little
The University of Melbourne

# Change detection project

This project is for the SFT analysis of a same-direction and opposite-direction change detection task.

The background of this study and preregistration is located [here](https://osf.io/e6nfg).


```{r readdata, echo=FALSE, warning=FALSE, message=FALSE, results="hide"}
# NOTE: Reference for adjusted rank transform test
# Leys, C., & Schumann, S. (2010). A nonparametric method to analyze interactions: The adjusted rank transform test. Journal of Experimental Social Psychology, 46, 684-688.


rm(list=ls())
library(tidyverse)
library(workflowr)
library(sft)
library(reshape2)
library(knitr)

## Reading data and variable names 
#define working directories
inputdir <- "data"

# list of subject directories storing data files
fnLoc = c('s1001', 's1114', 's1024', 's1911', 's2222')

# NOTE: when you add or remove subjects, you also need to:
# 1) Add a table to the ks_table section
# 2) Add the table to the mic_stats_table section
# 3) Add the table to the sic_stats_table section


nsubs = length(fnLoc)

# Column names
column_file      <- read.csv(paste(inputdir,"data_dictionary.csv",sep="/"), header = TRUE)

for (i in 1:length(fnLoc)){
   fp = file.path(inputdir, fnLoc) # File path 

   # Function to merge multiple .dat files
   mergeFiles = function(mypath, colfile){
      filenames=list.files(path=mypath, full.names=TRUE)
      datalist = lapply(filenames, function(x){read.table(file=x,header=FALSE, sep=",", col.names=colfile$column, comment.char="#")})
      bind_rows(datalist, .id = "column_label")
   }

   # All data
   data = mergeFiles(fp, column_file)
   # data = data[data$session == 11, ]

   if (i == 1){
      alldata = data
   } else {
      alldata = rbind(alldata, data)
   }
}

# Reorder data by session and trial
# data <- alldata[order(cbind(alldata$subject_id, alldata$session, alldata$trial_number)), ] 
data <- alldata[with(alldata, order(subject_id, session )), ]

# Remove timeouts [response ==9's]
ntimeouts = sum(data$response == 9)
data = data[data$response != 9, ]

data$item_condition = factor(trimws(data$item_condition), levels=c("HH", "HL", "LH", "LL", "HS", "LS", "SH", "SL", "SS"))

# Important variables
t = seq(0, 2, by=.01)
target_items = c("HH", "HL", "LH", "LL")
nbootstrap = 1000

# Check accuracy by session
bonusCutoff = .9
sessionAcc = aggregate(list('acc' = as.numeric(data$correct)), by=list("session" = data$session, 'sub_id' = data$subject_id), FUN=mean)
sessionAcc$cuttoff = sessionAcc$acc >= bonusCutoff
sessionAcc$bonusPerSession = sessionAcc$cuttoff * 3

bonusAmount = aggregate(list('amt' = sessionAcc$bonusPerSession), by = list('sub_id' = sessionAcc$sub_id), FUN=sum)

```

# Method

We tested `r nsubs` participants for 10 sessions: 5 sessions in the contrast swaps condition and 5 sessions in the contrast difference condition. One participant (s1114) completed 6 sessions of the contrast swaps condition.

```{r splitdata, echo=FALSE, warning=FALSE, message=FALSE, results="hide"}
# Split data into same_direction and opposite_direction conditions
swaps = data[data$condition == 1, ]
diffs = data[data$condition == 2, ]

# Trial counts for each item
n.swaps = aggregate(list('n' = as.numeric(swaps$correct)), by=list("subjects" = swaps$subject_id, "item" = swaps$item_condition), FUN=length)
n.swaps = n.swaps[order(n.swaps$subjects, n.swaps$item), ]

n.diffs = aggregate(list('n' = as.numeric(diffs$correct)), by=list("subjects" = diffs$subject_id, "item" = diffs$item_condition), FUN=length)
n.diffs = n.diffs[order(n.diffs$subjects, n.diffs$item), ]

n.count = rbind(spread(n.swaps, item, n), spread(n.diffs, item, n))
n.count$condition = c(rep("swaps", nsubs), rep("diffs", nsubs))
n.count = n.count[order(n.count$subjects), ]
n.count = n.count[, c('subjects', 'condition', 'HH', 'HL', 'LH', 'LL', 'HS', 'LS', 'SH', 'SL', 'SS')]

# Accuracy averages for each item
acc.swaps = aggregate(list('accuracy' = as.numeric(swaps$correct)), by=list("subjects" = swaps$subject_id, "item" = swaps$item_condition), FUN=mean)
acc.swaps = acc.swaps[order(acc.swaps$subjects, acc.swaps$item), ]
acc.swaps$accuracy = round(acc.swaps$accuracy, 2)

acc.diffs = aggregate(list('accuracy' = as.numeric(diffs$correct)), by=list("subjects" = diffs$subject_id, "item" = diffs$item_condition), FUN=mean)
acc.diffs = acc.diffs[order(acc.diffs$subjects, acc.diffs$item), ]
acc.diffs$accuracy = round(acc.diffs$accuracy, 2)

acc.mean = rbind(spread(acc.swaps, item, accuracy), spread(acc.diffs, item, accuracy))
acc.mean$condition = c(rep("swaps", nsubs), rep("diffs", nsubs))
acc.mean = acc.mean[order(acc.mean$subjects), ]
acc.mean = acc.mean[, c('subjects', 'condition', 'HH', 'HL', 'LH', 'LL', 'HS', 'LS', 'SH', 'SL', 'SS')]

# RT averages
rt.swaps = aggregate(list('rt' = swaps$rt[swaps$correct == 1]), by=list("subjects" = swaps$subject_id[swaps$correct == 1], "item" = swaps$item_condition[swaps$correct == 1]), FUN=mean)
rt.swaps = rt.swaps[order(rt.swaps$subjects, rt.swaps$item), ]
rt.swaps$rt = round(rt.swaps$rt, 3)

rt.diffs = aggregate(list('rt' = diffs$rt[swaps$correct == 1]), by=list("subjects" = diffs$subject_id[swaps$correct == 1], "item" = diffs$item_condition[swaps$correct == 1]), FUN=mean)
rt.diffs = rt.diffs[order(rt.diffs$subjects, rt.diffs$item), ]
rt.diffs$rt = round(rt.diffs$rt, 3)

rt.swaps.se = aggregate(list('sterr' = swaps$rt[swaps$correct == 1]), by=list("subjects" = swaps$subject_id[swaps$correct == 1], "item" = swaps$item_condition[swaps$correct == 1]), FUN=function(x)sd(x)/sqrt(length(x)))
rt.swaps.se = rt.swaps.se[order(rt.swaps.se$subjects, rt.swaps.se$item), ]
rt.swaps.se$sterr = round(rt.swaps.se$sterr, 5)

rt.diffs = aggregate(list('rt' = diffs$rt[swaps$correct == 1]), by=list("subjects" = diffs$subject_id[swaps$correct == 1], "item" = diffs$item_condition[swaps$correct == 1]), FUN=mean)
rt.diffs = rt.diffs[order(rt.diffs$subjects, rt.diffs$item), ]
rt.diffs$rt = round(rt.diffs$rt, 3)

rt.diffs.se = aggregate(list('sterr' = diffs$rt[diffs$correct == 1]), by=list("subjects" = diffs$subject_id[diffs$correct == 1], "item" = diffs$item_condition[diffs$correct == 1]), FUN=function(x)sd(x)/sqrt(length(x)))
rt.diffs.se = rt.diffs.se[order(rt.diffs.se$subjects, rt.diffs.se$item), ]
rt.diffs.se$sterr = round(rt.diffs.se$sterr, 5)

rt.mean = rbind(spread(rt.swaps, item, rt), spread(rt.diffs, item, rt))
rt.mean$condition = c(rep("swaps", nsubs), rep("diffs", nsubs))
rt.mean = rt.mean[order(rt.mean$subjects), ]
rt.mean = rt.mean[, c('subjects', 'condition', 'HH', 'HL', 'LH', 'LL', 'HS', 'LS', 'SH', 'SL', 'SS')]

# Error RT averages
ert.swaps = aggregate(list('rt' = swaps$rt[swaps$correct == 0]), by=list("subjects" = swaps$subject_id[swaps$correct == 0], "item" = swaps$item_condition[swaps$correct == 0]), FUN=mean)
ert.swaps = ert.swaps[order(ert.swaps$subjects, ert.swaps$item), ]
ert.swaps$rt = round(ert.swaps$rt, 3)
#if nrow(ert.swaps != 9){ 
#   
#   
#}

ert.diffs = aggregate(list('rt' = diffs$rt[swaps$correct == 0]), by=list("subjects" = diffs$subject_id[swaps$correct == 0], "item" = diffs$item_condition[swaps$correct == 0]), FUN=mean)
ert.diffs = ert.diffs[order(ert.diffs$subjects, ert.diffs$item), ]
ert.diffs$rt = round(ert.diffs$rt, 3)

ert.mean = rbind(spread(ert.swaps, item, rt), spread(ert.diffs, item, rt))
ert.mean$condition = c(rep("swaps", nsubs), rep("diffs", nsubs))
ert.mean = ert.mean[order(ert.mean$subjects), ]
ert.mean = ert.mean[, c('subjects', 'condition', 'HH', 'HL', 'LH', 'LL', 'HS', 'LS', 'SH', 'SL', 'SS')]

```

# Mean accuracy and response time for each item condition

We computed the mean accuracy and response time for each item in each condition.

```{r summary_table, echo=FALSE, warning=FALSE, message=FALSE, results="asis"}
kable(n.count, caption = "Trial Counts for each Item in Each Condition")
kable(acc.mean, caption = "Mean Accuracy for each Item in Each Condition")
kable(rt.mean, caption = "Mean Correct RT (sec) for each Item in Each Condition")
kable(ert.mean, caption = "Mean Error RT (sec) for each Item in Each Condition")
```

# Mean Interaction Contrasts

We plotted the double target items as a function of the discriminability in each location.

```{r plot_target_means, echo=FALSE, warning=FALSE, message=FALSE, results="asis"}

# Build data frame for plotting
s = cbind(rt.swaps[rt.swaps$item %in% target_items, ], "se" = rt.swaps.se$sterr[rt.swaps$item %in% target_items])
d = cbind(rt.diffs[rt.diffs$item %in% target_items, ], "se" = rt.diffs.se$sterr[rt.diffs$item %in% target_items])

s$condition = rep("swaps", nrow(s))
d$condition = rep("diffs", nrow(d))

s$d1 = substr(as.character(s$item), 1, 1)
s$d2 = substr(as.character(s$item), 2, 2)

d$d1 = substr(as.character(d$item), 1, 1)
d$d2 = substr(as.character(d$item), 2, 2)

df = rbind(s,d)
df$condition = as.factor(df$condition)
levels(df$condition) = c("swaps", "diffs")

# Default line plot
p <- ggplot(df, aes(x=d1, y=rt, group=d2)) + 
     geom_line(size = 1, aes(linetype=d2)) +
     geom_point(colour="black", size = 3, aes(fill=d2))+
     geom_errorbar(aes(ymin=rt-se, ymax=rt+se), width=.2)+
     facet_wrap(~subjects+condition, nrow=nsubs)

# Finished line plot
p = p+labs(title="Mean Response Times", x="Left Target", y = "RT (sec)")+
    scale_linetype_discrete(name  ="Right Target",
                         breaks=c("H", "L"),
                         labels=c("H", "L")) +
    scale_fill_discrete(name  ="Right Target",
                         breaks=c("H", "L"),
                         labels=c("H", "L"))
   
print(p)

```

```{r survivors, echo=FALSE, warning=FALSE, message=FALSE, results="hide"}
#subs = as.integer(substring(fnLoc, 2))
subs = unique(data$subject_id)
for (i in 1:nsubs){
   for (j in 1:length(target_items)){
      varname <- paste(fnLoc[i], "swaps", target_items[j], sep = ".")
      assign(varname, swaps$rt[swaps$subject_id == subs[i] & swaps$correct == 1 & swaps$item_condition %in% target_items[j]])
      evn <- paste('cdf', varname, sep='.')
      assign(evn, ecdf(eval(parse(text=varname))))
      
      
      varname <- paste(fnLoc[i], "diffs", target_items[j], sep = ".")
      assign(varname, diffs$rt[diffs$subject_id == subs[i] & diffs$correct == 1 & diffs$item_condition %in% target_items[j]])
      evn <- paste('cdf', varname, sep='.')
      assign(evn, ecdf(eval(parse(text=varname))))
   }
}
# Creates a series of functions names s1001.swaps.HH, s1001.diffs.HL, etc which are used to return a cdf by: s1001.swaps.HH(t)
```

```{r compute_sic, echo=FALSE, warning=FALSE, message=FALSE, results="hide"}
for (i in 1:nsubs){
   for (j in 1:length(target_items)){
      assignment <- paste("swaps.", target_items[j], '=', paste(fnLoc[i], "swaps", target_items[j], sep = "."), sep="")
      eval(parse(text=assignment))
      
      
      assignment <- paste("diffs.", target_items[j], '=', paste(fnLoc[i], "diffs", target_items[j], sep = "."), sep="")
      eval(parse(text=assignment))
   }
   varname <- paste('sic', fnLoc[i], "swaps", sep = ".")
   assign(varname, sic(HH=swaps.HH, HL=swaps.HL, LH=swaps.LH, LL=swaps.LL))
   varname <- paste('sic', fnLoc[i], "diffs", sep = ".")   
   assign(varname, sic(HH=diffs.HH, HL=diffs.HL, LH=diffs.LH, LL=diffs.LL))
}

```

We tested the interaction between the discriminability of the left target and right target using an adjusted rank transform test.

```{r mic_stats, echo=FALSE, warning=FALSE, message=FALSE, results="asis"}

get_mic <- function(x){
   mic = x[4]-x[3]-x[2]+x[1]
   return(mic)
} 


##
mic_test_table = 
   rbind(cbind("stat" = round(sic.s1001.swaps$MICtest$statistic,2), "p" = round(sic.s1001.swaps$MICtest$p.value,4)),
         cbind("stat" = round(sic.s1001.diffs$MICtest$statistic,2), "p" = round(sic.s1001.diffs$MICtest$p.value,4)))

rownames(mic_test_table) = NULL
mic_test_table.s1001 = as.data.frame(mic_test_table)
mic_test_table.s1001$condition = c("swaps", "diffs")
mic_test_table.s1001$mic = c(get_mic(rt.swaps$rt[rt.swaps$subjects ==  1001 & rt.swaps$item %in% target_items]),
                             get_mic(rt.diffs$rt[rt.swaps$subjects ==  1001 & rt.diffs$item %in% target_items]))
mic_test_table.s1001 = mic_test_table.s1001[c("condition", "mic", "stat", "p")]

kable(mic_test_table.s1001, caption = "Subject 1001: Adjusted Rank Transform test of the MIC")
   
##
mic_test_table = 
   rbind(cbind("stat" = round(sic.s1114.swaps$MICtest$statistic,2), "p" = round(sic.s1114.swaps$MICtest$p.value,4)),
         cbind("stat" = round(sic.s1114.diffs$MICtest$statistic,2), "p" = round(sic.s1114.diffs$MICtest$p.value,4)))

rownames(mic_test_table) = NULL
mic_test_table.s1114 = as.data.frame(mic_test_table)
mic_test_table.s1114$condition = c("swaps", "diffs")
mic_test_table.s1114$mic = c(get_mic(rt.swaps$rt[rt.swaps$subjects ==  1114 & rt.swaps$item %in% target_items]),
                             get_mic(rt.diffs$rt[rt.swaps$subjects ==  1114 & rt.diffs$item %in% target_items]))
mic_test_table.s1114 = mic_test_table.s1114[c("condition", "mic", "stat", "p")]

kable(mic_test_table.s1114, caption = "Subject 1114: Adjusted Rank Transform test of the MIC")

##
mic_test_table = 
   rbind(cbind("stat" = round(sic.s1024.swaps$MICtest$statistic,2), "p" = round(sic.s1024.swaps$MICtest$p.value,4)),
         cbind("stat" = round(sic.s1024.diffs$MICtest$statistic,2), "p" = round(sic.s1024.diffs$MICtest$p.value,4)))

rownames(mic_test_table) = NULL
mic_test_table.s1024 = as.data.frame(mic_test_table)
mic_test_table.s1024$condition = c("swaps", "diffs")
mic_test_table.s1024$mic = c(get_mic(rt.swaps$rt[rt.swaps$subjects ==  24 & rt.swaps$item %in% target_items]),
                             get_mic(rt.diffs$rt[rt.swaps$subjects ==  24 & rt.diffs$item %in% target_items]))
mic_test_table.s1024 = mic_test_table.s1024[c("condition", "mic", "stat", "p")]

kable(mic_test_table.s1024, caption = "Subject 1024: Adjusted Rank Transform test of the MIC")

##
mic_test_table = 
   rbind(cbind("stat" = round(sic.s1911.swaps$MICtest$statistic,2), "p" = round(sic.s1911.swaps$MICtest$p.value,4)),
         cbind("stat" = round(sic.s1911.diffs$MICtest$statistic,2), "p" = round(sic.s1911.diffs$MICtest$p.value,4)))

rownames(mic_test_table) = NULL
mic_test_table.s1911 = as.data.frame(mic_test_table)
mic_test_table.s1911$condition = c("swaps", "diffs")
mic_test_table.s1911$mic = c(get_mic(rt.swaps$rt[rt.swaps$subjects == 911 & rt.swaps$item %in% target_items]),
                             get_mic(rt.diffs$rt[rt.swaps$subjects == 911 & rt.diffs$item %in% target_items]))
mic_test_table.s1911 = mic_test_table.s1911[c("condition", "mic", "stat", "p")]

kable(mic_test_table.s1911, caption = "Subject 1911: Adjusted Rank Transform test of the MIC")

##
mic_test_table = 
   rbind(cbind("stat" = round(sic.s2222.swaps$MICtest$statistic,2), "p" = round(sic.s2222.swaps$MICtest$p.value,4)),
         cbind("stat" = round(sic.s2222.diffs$MICtest$statistic,2), "p" = round(sic.s2222.diffs$MICtest$p.value,4)))

rownames(mic_test_table) = NULL
mic_test_table.s2222 = as.data.frame(mic_test_table)
mic_test_table.s2222$condition = c("swaps", "diffs")
mic_test_table.s2222$mic = c(get_mic(rt.swaps$rt[rt.swaps$subjects == 2222 & rt.swaps$item %in% target_items]),
                             get_mic(rt.diffs$rt[rt.swaps$subjects == 2222 & rt.diffs$item %in% target_items]))
mic_test_table.s2222 = mic_test_table.s2222[c("condition", "mic", "stat", "p")]

kable(mic_test_table.s2222, caption = "Subject 2222: Adjusted Rank Transform test of the MIC")

```

# Test of stochastic dominance

We tested the ordering of the survivor functions using a series of Kolmogorov-Smirnoff test. If stochastic dominance is preserved, then we expect the first four tests to be significant while the second four tests are not.

```{r Splot, echo=FALSE, warning=FALSE, message=FALSE, results="asis"}
cols = c("red", "red", "blue", "blue")
ltys = c(1, 2, 2, 1)


 par("mar")
 par(mar=c(1,1,1,1))
par(mfrow=c(nsubs,2)) 

for (i in 1:nsubs){
   # Plot swaps condition
   for (j in 1:length(target_items)){
      varname <- paste('cdf', fnLoc[i], "swaps", target_items[j], sep = ".")
      ft = 1-eval(parse(text=paste(varname, "(t)", sep="")))
      if (j == 1){
         plot(t, ft, type="l", col=cols[j], lwd=2, lty = ltys[j], xlab="t (sec)", ylab="X=S(t)")
      } else {
         lines(t, ft, type="l", col=cols[j], lwd=2, lty = ltys[j])
      }
   }
   title(paste(fnLoc[i], ": Contrast Swaps", sep=""))
   legend(1.5, 1, legend=c("HH", "HL", "LH", "LL"), lwd=2, col=cols, lty=ltys, cex=0.8)

   # Plot diffs condition
   for (j in 1:length(target_items)){
      varname <- paste('cdf', fnLoc[i], "diffs", target_items[j], sep = ".")
      ft = 1-eval(parse(text=paste(varname, "(t)", sep="")))
      if (j == 1){
         plot(t, ft, type="l", col=cols[j], lwd=2, lty = ltys[j], xlab="t (sec)", ylab="X=S(t)")
      } else {
         lines(t, ft, type="l", col=cols[j], lwd=2, lty = ltys[j])
      }
   }
   title(paste(fnLoc[i], ": Contrast Differences", sep=""))
   legend(1.5, 1, legend=c("HH", "HL", "LH", "LL"), lwd=2, col=cols, lty=ltys, cex=0.8)
}

```

```{r ks_table, echo=FALSE, warning=FALSE, message=FALSE, results="asis"}
ksrows = as.data.frame(eval(parse(text=paste("sic.", fnLoc[1], ".swaps$Dominance$Test", sep=""))))
ks = vector(mode = "list", length = nsubs)
for (i in 1:nsubs){
   kstable = cbind(ksrows, 
                   round(eval(parse(text=paste("sic.", fnLoc[i], ".swaps$Dominance$statistic", sep=""))), 3),
                   round(eval(parse(text=paste("sic.", fnLoc[i], ".swaps$Dominance$p.value", sep=""))), 3),
                   round(eval(parse(text=paste("sic.", fnLoc[i], ".diffs$Dominance$statistic", sep=""))), 3),
                   round(eval(parse(text=paste("sic.", fnLoc[i], ".diffs$Dominance$p.value", sep=""))), 3))
   names(kstable) = c("Test", "ks.swaps", "p.swaps", "ks.diffs", "p.diffs")
   ks[[i]] = kstable
}

# Note: duplicate this line for each subject
kable(ks[[1]], caption = paste("Stochastic Dominance tests for subject", fnLoc[1]))
kable(ks[[2]], caption = paste("Stochastic Dominance tests for subject", fnLoc[2]))
kable(ks[[3]], caption = paste("Stochastic Dominance tests for subject", fnLoc[3]))
kable(ks[[4]], caption = paste("Stochastic Dominance tests for subject", fnLoc[4]))
kable(ks[[5]], caption = paste("Stochastic Dominance tests for subject", fnLoc[5]))

```

# Survivor Interaction Contrasts

```{r bootstrap_sic, echo=FALSE, warning=FALSE, message=FALSE, results="hide"}

sicbootstrap <- function(HH, HL, LH, LL, t, nbootstrap){
# sicbootstrap returns a bootstrapped sample from the 4 data vectors:
# HH, HL, LH, and LL to compute std_boot, which is the std. confidence interval for SIC(t)
# You can choose other C.I. using percentiles (e.g., 90%)
#
# Ami Eidels, AMPC 2011

# n iterations of resmapling
# ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
  sic_boot = matrix(NA, nrow=nbootstrap,ncol=length(t))
  for (n in 1:nbootstrap){
        HH_boot = sample(HH, length(HH), replace=TRUE)
        HL_boot = sample(HL, length(HL), replace=TRUE)
        LH_boot = sample(LH, length(LH), replace=TRUE)
        LL_boot = sample(LL, length(LL), replace=TRUE)

        Shh_boot = 1-ecdf(HH_boot)(t)
        Shl_boot = 1-ecdf(HL_boot)(t)
        Slh_boot = 1-ecdf(LH_boot)(t)
        Sll_boot = 1-ecdf(LL_boot)(t)

        sic_boot[n, ] = Shh_boot - Shl_boot - Slh_boot + Sll_boot

  }

   std_boot = apply(sic_boot, 2, FUN=sd)
   return(std_boot)
}

for (i in 1:nsubs){
      outname <- paste(fnLoc[i], "swaps", "sic.std", sep = ".")
      hh <- eval(parse(text=paste(fnLoc[i], "swaps", "HH", sep = ".")))
      hl <- eval(parse(text=paste(fnLoc[i], "swaps", "HL", sep = ".")))
      lh <- eval(parse(text=paste(fnLoc[i], "swaps", "LH", sep = ".")))
      ll <- eval(parse(text=paste(fnLoc[i], "swaps", "LL", sep = ".")))
      
      assign(outname, sicbootstrap(hh, hl, lh, ll, t, nbootstrap))

      outname <- paste(fnLoc[i], "diffs", "sic.std", sep = ".")
      hh <- eval(parse(text=paste(fnLoc[i], "diffs", "HH", sep = ".")))
      hl <- eval(parse(text=paste(fnLoc[i], "diffs", "HL", sep = ".")))
      lh <- eval(parse(text=paste(fnLoc[i], "diffs", "LH", sep = ".")))
      ll <- eval(parse(text=paste(fnLoc[i], "diffs", "LL", sep = ".")))
      
      assign(outname, sicbootstrap(hh, hl, lh, ll, t, nbootstrap))
}

```

We tested the architecture underlying change detection decision using the survivor interaction contrast.

```{r sic_plot, echo=FALSE, warning=FALSE, message=FALSE, results="asis"}
# Build data file for ggplot
# subject, condition, t, sic

con1   = rep(1, length(t))
con2   = rep(2, length(t))
concol = c(con1, con2)

tcol = c(t,t)

for (i in 1:nsubs){
   # Plot swaps condition
   varname <- paste(paste('sic', fnLoc[i], "swaps", sep = "."), "SIC", sep = "$")
   sic1 = eval(parse(text=paste(varname, "(t)", sep="")))
   sic1lo = sic1 - 2*eval(parse(text=paste(fnLoc[i], "swaps", "sic.std", sep=".")))
   sic1hi = sic1 + 2*eval(parse(text=paste(fnLoc[i], "swaps", "sic.std", sep=".")))
   
   varname <- paste(paste('sic', fnLoc[i], "diffs", sep = "."), "SIC", sep = "$")
   sic2 = eval(parse(text=paste(varname, "(t)", sep="")))
   sic2lo = sic2 - 2*eval(parse(text=paste(fnLoc[i], "diffs", "sic.std", sep=".")))
   sic2hi = sic2 + 2*eval(parse(text=paste(fnLoc[i], "diffs", "sic.std", sep=".")))

   siccol = c(as.array(sic1), as.array(sic2))
   siclocol = c(as.array(sic1lo), as.array(sic2lo))
   sichicol = c(as.array(sic1hi), as.array(sic2hi))
   
   subcol = rep(subs[i], length(tcol))
   
   if (i == 1){
      sic.plot.data = as.data.frame(cbind("subject" = subcol, "condition" = concol, "t" = tcol, "SIC" = siccol, "SIClo" = siclocol, "SIChi" = sichicol))      
   } else {
      newsub = as.data.frame(cbind("subject" = subcol, "condition" = concol, "t" = t, "SIC" = siccol, "SIClo" = siclocol, "SIChi" = sichicol))                  
      sic.plot.data = rbind(sic.plot.data, newsub)
   }
}

sic.plot.data$condition = as.factor(sic.plot.data$condition)
levels(sic.plot.data$condition) = c("swaps", "diffs")
#sic.plot.data$condition[sic.plot.data$condition == 1] = "swaps"
#sic.plot.data$condition[sic.plot.data$condition == 2] = "diffs"

sicp = ggplot(data=sic.plot.data, aes(x=t, y=SIC)) +
  geom_ribbon(aes(ymin=SIClo, ymax=SIChi), fill="steelblue2", color="steelblue2") + 
  geom_line(color="red")+
  facet_wrap(~subject+condition, nrow=nsubs) +
  ggtitle('Survivor Interaction Contrasts')

print(sicp)
```
We tested the significance of the positive and negative SIC regions using the Houpt-Townsend D+ and D- statistics.

```{r sic_stats_table, echo=FALSE, warning=FALSE, message=FALSE, results="asis"}

sic_test_table = 
   rbind(cbind("stat" = round(sic.s1001.swaps$SICtest$positive$statistic,2), "p" = round(sic.s1001.swaps$SICtest$positive$p.value,2)),
         cbind("stat" = round(sic.s1001.swaps$SICtest$negative$statistic,2), "p" = round(sic.s1001.swaps$SICtest$negative$p.value,2)),
         cbind("stat" = round(sic.s1001.diffs$SICtest$positive$statistic,2), "p" = round(sic.s1001.diffs$SICtest$positive$p.value,2)),
         cbind("stat" = round(sic.s1001.diffs$SICtest$negative$statistic,2), "p" = round(sic.s1001.diffs$SICtest$negative$p.value,2)))

rownames(sic_test_table) = NULL
sic_test_table.s1001 = as.data.frame(sic_test_table)
sic_test_table.s1001$condition = c("swaps", "swaps", "diffs", "diffs")
sic_test_table.s1001$test = c("D+", "D-", "D+", "D-")
sic_test_table.s1001 = sic_test_table.s1001[c("condition", "test", "stat", "p")]

kable(sic_test_table.s1001, caption = "SIC tests for subject 1001")
   

sic_test_table = 
   rbind(cbind("stat" = round(sic.s1114.swaps$SICtest$positive$statistic,2), "p" = round(sic.s1114.swaps$SICtest$positive$p.value,2)),
         cbind("stat" = round(sic.s1114.swaps$SICtest$negative$statistic,2), "p" = round(sic.s1114.swaps$SICtest$negative$p.value,2)),
         cbind("stat" = round(sic.s1114.swaps$SICtest$positive$statistic,2), "p" = round(sic.s1114.swaps$SICtest$positive$p.value,2)),
         cbind("stat" = round(sic.s1114.swaps$SICtest$negative$statistic,2), "p" = round(sic.s1114.swaps$SICtest$negative$p.value,2)))

rownames(sic_test_table) = NULL
sic_test_table.s1114 = as.data.frame(sic_test_table)
sic_test_table.s1114$condition = c("swaps", "swaps", "diffs", "diffs")
sic_test_table.s1114$test = c("D+", "D-", "D+", "D-")
sic_test_table.s1114 = sic_test_table.s1114[c("condition", "test", "stat", "p")]
kable(sic_test_table.s1114, caption = "SIC tests for subject 1114")

## 1024
sic_test_table = 
   rbind(cbind("stat" = round(sic.s1024.swaps$SICtest$positive$statistic,2), "p" = round(sic.s1024.swaps$SICtest$positive$p.value,2)),
         cbind("stat" = round(sic.s1024.swaps$SICtest$negative$statistic,2), "p" = round(sic.s1024.swaps$SICtest$negative$p.value,2)),
         cbind("stat" = round(sic.s1024.swaps$SICtest$positive$statistic,2), "p" = round(sic.s1024.swaps$SICtest$positive$p.value,2)),
         cbind("stat" = round(sic.s1024.swaps$SICtest$negative$statistic,2), "p" = round(sic.s1024.swaps$SICtest$negative$p.value,2)))

rownames(sic_test_table) = NULL
sic_test_table.s1024 = as.data.frame(sic_test_table)
sic_test_table.s1024$condition = c("swaps", "swaps", "diffs", "diffs")
sic_test_table.s1024$test = c("D+", "D-", "D+", "D-")
sic_test_table.s1024 = sic_test_table.s1024[c("condition", "test", "stat", "p")]
kable(sic_test_table.s1024, caption = "SIC tests for subject 1024")

## 1911
sic_test_table = 
   rbind(cbind("stat" = round(sic.s1911.swaps$SICtest$positive$statistic,2), "p" = round(sic.s1911.swaps$SICtest$positive$p.value,2)),
         cbind("stat" = round(sic.s1911.swaps$SICtest$negative$statistic,2), "p" = round(sic.s1911.swaps$SICtest$negative$p.value,2)),
         cbind("stat" = round(sic.s1911.swaps$SICtest$positive$statistic,2), "p" = round(sic.s1911.swaps$SICtest$positive$p.value,2)),
         cbind("stat" = round(sic.s1911.swaps$SICtest$negative$statistic,2), "p" = round(sic.s1911.swaps$SICtest$negative$p.value,2)))

rownames(sic_test_table) = NULL
sic_test_table.s1911 = as.data.frame(sic_test_table)
sic_test_table.s1911$condition = c("swaps", "swaps", "diffs", "diffs")
sic_test_table.s1911$test = c("D+", "D-", "D+", "D-")
sic_test_table.s1911 = sic_test_table.s1911[c("condition", "test", "stat", "p")]
kable(sic_test_table.s1911, caption = "SIC tests for subject 1911")

## 2222
sic_test_table = 
   rbind(cbind("stat" = round(sic.s2222.swaps$SICtest$positive$statistic,2), "p" = round(sic.s2222.swaps$SICtest$positive$p.value,2)),
         cbind("stat" = round(sic.s2222.swaps$SICtest$negative$statistic,2), "p" = round(sic.s2222.swaps$SICtest$negative$p.value,2)),
         cbind("stat" = round(sic.s2222.swaps$SICtest$positive$statistic,2), "p" = round(sic.s2222.swaps$SICtest$positive$p.value,2)),
         cbind("stat" = round(sic.s2222.swaps$SICtest$negative$statistic,2), "p" = round(sic.s2222.swaps$SICtest$negative$p.value,2)))

rownames(sic_test_table) = NULL
sic_test_table.s2222 = as.data.frame(sic_test_table)
sic_test_table.s2222$condition = c("swaps", "swaps", "diffs", "diffs")
sic_test_table.s2222$test = c("D+", "D-", "D+", "D-")
sic_test_table.s2222 = sic_test_table.s2222[c("condition", "test", "stat", "p")]
kable(sic_test_table.s2222, caption = "SIC tests for subject 2222")

```

```{r sic_group_code, echo=FALSE, warning=FALSE, message=FALSE, results="hide"}
# # Extract double targets
# doubletargets = c("HH", "HL", "LH", "LL")
# dt.swaps = swaps[grep(paste(doubletargets, collapse="|"), swaps$item_condition), ]
# dt.diffs = swaps[grep(paste(doubletargets, collapse="|"), diffs$item_condition), ]
# 
# # Extract RTs
# data2sic = function(datatable){
#     rt.HH = datatable$rt[trimws(as.character(datatable$item_condition)) == "HH" & datatable$correct == 1]*1000
#     rt.HL = datatable$rt[trimws(as.character(datatable$item_condition)) == "HL" & datatable$correct == 1]*1000
#     rt.LH = datatable$rt[trimws(as.character(datatable$item_condition)) == "LH" & datatable$correct == 1]*1000
#     rt.LL = datatable$rt[trimws(as.character(datatable$item_condition)) == "LL" & datatable$correct == 1]*1000
#    
#     sic(rt.HH, rt.HL, rt.LH, rt.LL)
#  }
#  
#  sic.swaps = data2sic(dt.swaps)
#  sic.diffs = data2sic(dt.diffs)
#  
#  # Plot
#  plot(sic.swaps$SIC, do.p=FALSE, ylim=c(-.5,.5))
#  plot(sic.diffs$SIC, do.p=FALSE, ylim=c(-.5,.5))
# 
# ## Set up data into standard form
# # standard = matrix(data=NA, nrow=nrow(swaps), ncol=ncol(swaps))
#  toStandardForm = function(datatable, condition){
#    standard_mat = matrix(data=NA, nrow=nrow(datatable), ncol=6)
#    colnames(standard_mat) <- c("Subject", "Condition", "RT", "Correct", "Channel1", "Channel2")
#    rownames(standard_mat) <- 1:nrow(datatable)
#    standard <- as.data.frame(standard_mat)
#    
#    standard$Subject = datatable$subject
#    standard$Condition = rep("OR", nrow(standard))
#    standard$RT = datatable$rt*1000
#    standard$Correct = datatable$correct
#    standard$Channel1[grep(paste(c("SS", "SL", "SH"), collapse="|"), datatable$item_condition)] = 0
#    standard$Channel1[grep(paste(c("LS", "LL", "LH"), collapse="|"), datatable$item_condition)] = 1
#    standard$Channel1[grep(paste(c("HS", "HL", "HH"), collapse="|"), datatable$item_condition)] = 2
#    
#    standard$Channel2[grep(paste(c("SS", "LS", "HS"), collapse="|"), datatable$item_condition)] = 0
#    standard$Channel2[grep(paste(c("SL", "LL", "HL"), collapse="|"), datatable$item_condition)] = 1
#    standard$Channel2[grep(paste(c("SH", "LH", "HH"), collapse="|"), datatable$item_condition)] = 2
#    return(standard)
# }
# 
# sicdata.swaps = toStandardForm(swaps, "OR")
# sicdata.diffs = toStandardForm(diffs, "OR") 
# sicdata.diffs$Subject = sicdata.diffs$Subject+10000
# 
# sicdata = rbind(sicdata.swaps, sicdata.diffs)
# sic.results = sicGroup(sicdata)


```


